
\chapter{Topology}
\section{Basics}
\subsection{Quickies}
\begin{itemize}
\item
Two important things topology allows us to talk about are?
\item
Definition of topology?
\item
Definition of topological space?
\item
Chaotic and discrete topology.
\item
Coarser and finer topology.
\item
What is an open set with respect to a topology?
\item
Standard topology. Does it have to be defined on $R^{n}$? Open sets in standard
topology.
\item
Induced topology \ Subset topology.
\item
Quotient topology.
\item
Define the $S^{1}$ topology as an induced topology from $R^{2}$ and a quotient topology of $R$.
\item
Product topology.
\item
What is a sequence (A sequence in $M$)? Complete : A sequence q in M is said to converge against a limit point $a \in M$ if:
\item
In a discrete topology all singleton sets are open $\implies$ all converging sequences are?
\item
Define continuity.
\item
Show that a map $\phi : M \rightarrow N $ is always continuous if either $O_{M}$ is discrete or $O_{N}$ is chaotic.
\item
Homeomorphism or structure preserving maps. Homeomorphic or topologically isomorphic. \\

$(M,O_{M}) \cong_{top} (N,O_{N}) \implies M \cong_{set} N$


\end{itemize}

\section{In variants of a topological space}
\subsection{Quickies}

\begin{itemize}
\item
Define $T1$ and $T2$. Zariski topology is?
\item
What is a cover and an open cover. Does open cover depend on the topology, what about the cover?
\item
What is a compact topological space?
\item
If $(M,O_{M})$ is a topological space and $N \subset M$ the it is called compact if $(N,O\mid_{N})$ is compact.
\item
$Heine-Borel$ \index{Heine-Borel} theorem.
\item
What is a metric space? Define an open ball. Using it induce a natural topological structure on the parent set. How is this topology related to the standard topology?
\item
What is the difference between totally bounded and bounded? How are these notions different in an euclidian space? What is a complete space?
\item
What is the general statement of $Heine-Borel$ in the above setting.
\item
If the constituent topological spaces are compact then the product topological space is?
\item
What is a refinement of a cover? When is it open and locally finite?
\item
A topological space is called \index{paracompact}$paracompact$ if every open cover has an open refinement that is locally finite.
\item
What is a mertisable topological space? How is it related to a paracompact space? $Stone theorem$
\item
Product topological space of a compact and a paracompact space is paracompact.
\item
What is partition of unity of a set? 
\item
A partition of unity set $F$ called subordinate to a cover $C$ if: 
\[\forall f \in F:\exists U \in C: f(x) \neq 0 \Rightarrow x \in U.\]

\item
Let $(M,O_{M})$ be a Hausdorff topological space. Then $(M,O_{M})$ is paracompact if, and only if, every open cover admits a partition of unity subordinate to that cover.

\item 
What is a connected topological space?

\item 
If the only subsets that are both open and closed are $ \phi $ and $ M $ then the topological space is? Is the converse true?


\item 

Path connected: 
$ (M,O_{m})$ is called path connected if $ \forall p,q \in M $there exists a continuous curve $ \gamma : [0,1] \rightarrow  M $ such that  $ \gamma(0) = p$and $ \gamma(1) = q $.

\item 
Consider the function $ \gamma(\lambda) := p+ \lambda(q-p) $. Why is it not a proof of the fact that every topological space is path connected?

\item 
Does $ Path connected \implies Connected $? What about the reverse? Give an example.

\item 
\textbf{Homotopic curves}
Let $(M,O_{M})$ be a topological space. Two curves $\gamma,\delta :[0,1]\to M$ such that:

$\gamma(0)=\delta(0) \quad and \quad \gamma(1)=\delta(1)$

are said to be \emph{homotopic}\index{homotopic curves} if there exists a continuous map $h : [0,1]\times[0,1]\to M$ such that for all $\l \in [0,1]$:

$h(0,\lambda) = \gamma(\lambda) \quad and \quad h(1,\lambda)=\delta(\lambda).$

\item 
Argue that being homotopic is an equivalence relation.

\item 
\textbf{Space of loops} Defined for all $ p \in M $\\

$\mathscr{L}_{p} := {\gamma:[0,1]\to M \mid \gamma \text{ is continuous and } \gamma(0) = \gamma(1) }$

\item 
\textbf{Concatenation operator, $ * : \mathscr{L}_{p} \times \mathscr{L}_{p} \to \mathscr{L}_{p}  $} :\\
\[
 (\gamma * \delta)(\lambda) :=
\begin{cases}
\gamma(2\lambda) & \text{if } 0\leq \lambda \leq \dfrac{1}{2}\\
\delta(2\lambda -1) & \text{if }\dfrac{1}{2} \leq \lambda \leq 1
\end{cases}
\]









\end{itemize}



